Timely Object Detection

### 2012-03-05 writeups/eccv12/technical.tex
mrf section done

\section{Multi-class Recognition Policy}
\begin{figure}[h!]
\center{\includegraphics[width=0.66\linewidth]
    {figures/pomdp.pdf}}
  \caption{Summary of our approach to the problem. Our system has two major parts: (1) selecting an action by predicting its value; (2) updating the belief state with observations resulting from the action.}
  \label{fig:pomdp}
\end{figure}

@@

\subsection{The model of the belief state}
\begin{figure}[h!]
\centering
\includegraphics[width=0.56\linewidth]{figures/inf_model_mrf.pdf}
\caption{
We present a point in the middle of the decision process for 3 classes.
Some classifiers have already been observed.
}
\label{fig:model}
\end{figure}

@@

We employ a fully-connected Markov Random Field (MRF), as shown in Figure~\ref{fig:model}.
The parameters are trained on fully-observed data.
Exact inference is of course intractable in a general model of this type, and quite slow for a model of our size.
Instead, we use Loopy Belief Propagation, which provides no general convergence guarantees but has been shown to work well empirically \todo{cite}.
The implementations details are given further in \autoref{sec:implementation}.

@@

\subsubsection{Learning the greedy policy}
We note that we can represent the one-step greedy policy value function as a scalar product

\subsubsection{Learning the proper policy}
\note{I'm considering two options here: (1) log-linear representation and policy gradient algorithm; (2) least-squares policy iteration.}

\paragraph{Policy gradient algorithm}
We redefine our policy as picking the mode of a log-linear parametrized distribution:
\begin{equation}
P(a|b;\theta) = \frac{\exp(\theta^T \phi(b,a))}{\sum_{a' \in \mathcal{A}} \exp(\theta^T \phi(b,a')}
\end{equation}

Basically stochastic gradient ascent on the estimate of the reward accrued by an episode.

This approach has been shown to scale to large problems in \cite{Branavan2009}, although it has been proven to converge only to local maxima and only for MDPs \cite{Sutton2000}.

\note{Does the constraint that no action is taken more than once affect this algorithm?}

\paragraph{Least-squares Policy Iteration}
An efficient form of temporal-difference learning used in \cite{Kwok2004}.
Policy remains parameterized as it was.

\section{Implementation Details and Evaluation} \label{sec:implementation}
We use FastInf \cite{Jaimovich2010} for learning and inference in our MRF model.
The real-valued classifier responses $o_i$ are discretized into data-dependent bins for efficiency.

>>>>

\section{Multi-class Recognition Policy} \label{sec:tech}
\begin{figure}[h!]
\center{\includegraphics[width=0.66\linewidth]
    {figures/pomdp.pdf}}
  \caption{Summary of our approach to the problem. Our system has two major parts: (1) selecting an action by predicting its value; (2) updating the belief state with observations resulting from the action.}
  \label{fig:pomdp}
\end{figure}

@@

\subsection{The model of the belief state}
\begin{figure}[h!]
\centering
\includegraphics[width=0.56\linewidth]{figures/inf_model_mrf_1.pdf}
\caption{
We present a point in the middle of the decision process for 3 classes; one action has already been taken.
\comment{Some classifiers have already been observed.}
}
\label{fig:model}
\end{figure}

@@

We employ a fully-connected Markov Random Field (MRF), as shown in Figure~\ref{fig:model}.
The $L_i$ variables are discretized from real-valued responses of a classifier on the detections output by the deformable part-model detector we employ (see Section~\ref{sec:tech}).

The classifier is a linear kernel SVM on the top two max detection scores in the list of detections.
The responses are discretized per variable based on the distribution of the scores on the training dataset.

The MRF is implemented with an open-source graphical model package \cite{Jaimovich2010}.
The parameters of the model are trained on fully-observed data.
Exact inference is generally intractable in this model.
Instead, we use Loopy Belief Propagation, which does not provide general convergence guarantees but has been shown to work well empirically on similar tasks \todo{cite}.

\todo{what to say about cost of inference? realistically it's 0.5 seconds while the detection action + classification is about 2 seconds.}

@@

\subsubsection{Learning the weights}
We note that we can represent the one-step greedy policy value function as a scalar product
